First exclusive DVCS measurement off bound nucleon in $^4$He

### 2018-02-19 eg6-letters/incoherent/incoherent_prl.tex
edit figure 5 by including the coherent points

\begin{figure}[tb]
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
   represent the statistical uncertainties, while the gray bands represent the 
   systematic uncertainties. On the middle plot: the curves are theoretical 
   calculations from \cite{simonetta_2}. On the bottom: the green circles are 
   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
   \cite{Airapetian}, the curves represent theoretical calculations from 
   \cite{simonetta_2}. } \label{fig:alu90}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (top), $x_B$ (middle), and $t$ 
   (bottom). The black squares are from this work, the green circles are the 
   HERMES inclusive measurement \cite{Airapetian}. The blue and red curves are 
   results of off-shell calculations \cite{simonetta_2}. The solid and dashed 
   black curves are from on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

>>>>

\begin{figure}[tb]
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
   represent the statistical uncertainties, while the gray bands represent the 
   systematic uncertainties. On the middle plot: the curves are theoretical 
   calculations from \cite{simonetta_2}. On the bottom: the solid (empty) green 
   circles are the HERMES $-A_{LU}$ (positron beam was used) inclusive 
measurements for the incoherent (coherent) enriched region 
\cite{Airapetian:2009cga}, the curves represent theoretical calculations from 
\cite{simonetta_2}.  } \label{fig:alu90}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (top), $x_B$ (middle), and $t$ 
   (bottom). The black squares are from this work, the green circles are the 
HERMES inclusive measurement \cite{Airapetian:2009cga}. The blue and red curves 
are results of off-shell calculations \cite{simonetta_2}. The solid and dashed 
black curves are from on-shell calculations \cite{Guzey:2008fe}.} 
\label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}
